---
title: "R Classes and Objects"
output: html_notebook
---


1. S3 Class 
2. S4 Class 
3. Reference Class


```{r}
#S3 Class  

#create a list with required variables

emp = list(name="abc",dept="IT",salary=10000) 

#name the class 

class(emp) = "employee"


```
Checking the type of employee
```{r}
class(emp)
```
```{r}
#S4 Class 

#setClass() generates s4 class and we can create objects new() 

setClass("employee",slots = list(name="character",dept="character",salary="numeric"))

```

```{r}
#Reference Class 
setRefClass("employeee")
```

### S3 Class 

```{r}

emp = list(name="abc",dept="IT",salary=10000) 

#name the class 

class(emp) = "employee"
```
```{r}
emp
```
Constructor in S3 class

```{r}
employee = function(n,d,s){
  value = list(name=n,dept=d,salary=s) #setting class values 
  attr(value,"class") ="employee" #class of value to employee
  value # returning value
}
```
```{r}
e = employee("Alex","Dev",20000)
e
```
### How to Write Method
```{r}
print.employee = function(obj){
  cat("Employee name is",obj$name,"\n")
  cat("Employee Department is",obj$dept,"\n")
  cat("Employee Salary is",obj$salary,"\n")
}
```
Running our own print method
```{r}
print(e)
```
```{r}
salarydata.employee <- function(obj) {
cat("Your salary is", obj$salary, "\n")
}

```
```{r}
salarydata.employee(e) 
```
## S4 Class 


```{r}
#Creating S4 class

student=setClass("student",slots = list(name="character",age="numeric",marks="numeric"))
```
```{r}
#Creating Objects in S4 class

stud1= new("student",name="Alex",age=24,marks=56)
stud1
```
```{r}
isS4(e)
```
```{r}
#generator function
stud2=student(name="Jae",age=23,marks=56)
stud2
```
Object is accessed using @ 

### Accessing Slots
```{r}
stud1@name
stud2@name

```
### Modifying Slots 
```{r}
stud1@marks = 78
stud1
```
```{r}
# using slots function to modify value 
slot(stud1,"name")

slot(stud1,"name") = "Alexa"

slot(stud1,"name")
```
### How to generate S4 method 

```{r}
#for writing our own s4 function we have to use setMethod() function.

setMethod("show","student",function(obj){
  cat("Name is ",obj@name,"\n")
  cat("Age is ",obj@age,"years \n")
  cat("Marks is ",obj@marks,"\n")
}
)
```
```{r}
stud1
```
```{r}
isS4(show)
```
```{r}
setGeneric(name="setMarks",def=function(obj,mark){
  standardGeneric("setMarks")
})
setMethod(f="setMarks","student",function(obj,mark){
  obj@marks= mark
  validObject(obj)
  obj
}
)
```

```{r}
setMarks(stud1,90)
```
## Reference Class

```{r}
#using setRefClass for creating ref class 

customer = setRefClass("customer",fields = list(name="character",contact="character",category="character",age="numeric",gender="character"))


```
create objects of reference class
```{r}
c = customer(name="John",contact="1234567890",category="Sports",age=26,gender="Male")
c

```
Accessing Class Variables

```{r}
#object_name$variable_name 
c$name
c$age
```
```{r}
x = list("a"=4,"b"=6)
y=x


y$a=10

x # x is not changeing 
y # y value is getting changed
```

```{r}

x =customer(name="Alex",contact="1234567890",category="Sports",age=26,gender="Male")
y=x

y$name ="Jae"  #y value  i s changing 
x # x is also changing
y
```
```{r}
x = customer(name="Alex",contact="1234567890",category="Sports",age=26,gender="Male")

y = x$copy() 

y$name="max"

```
```{r}
x
y
```
### Reference Methods 

```{r}
customer = setRefClass("customer",
fields = list(name="character",contact="character",category="character",age="numeric",gender="character"),
methods = list(
  changeContact=function(cont){
  contact <<- cont  #non local assignment operator for class variable
  },
  customerDetails= function(){
    cat(age,"\n")
    cat(category,"\n")
    cat(gender,"\n")
  }
  )
)
```
```{r}
c1 =customer(name="Alex",contact="1234567890",category="Sports",age=26,gender="Male")
c1
```
```{r}
c1$changeContact("111111111")
```
```{r}
c1
```
```{r}
c1$customerDetails()
```
## Inheritance in R 

### S3 Class Inheritance
```{r}
 parent = list(name="abc",data="parent class")
class(parent) ="parent"
parent
```
```{r}
print.parent = function(obj){
  cat(obj$name,"\n")
  cat("this is ",obj$data,"\n")
}
```
```{r}
print(parent)
```
### Deriving child class using parent class in S3 

```{r}
child = list(name="xyz",data="child class")
class(child) =c("child","parent") # own class,parent class
child
```
```{r}
print.child= function(obj){
  cat(obj$name," is a object of ",obj$data)
}
```
```{r}
child
```

```{r}
inherits(child,"parent")
is(child,"parent")
```
### S4 Inheritance in R
```{r}
employee =setClass("employee",slots = list(name="character",dept="character",salary="numeric"))
employee
```
```{r}
e1= employee(name="Alex",dept="IT",salary=20000)
e1
```
```{r}
overseasEmployee= setClass("overseasEmployee",slots=list(country="character"),contains = "employee")
overseasEmployee
```

```{r}
oe = overseasEmployee(name="John",dept="Finance",salary=30000,country = "USA")
oe
```
### Inheritance in Reference Class 
```{r}
customer = setRefClass("customer",
fields = list(name="character",contact="character",category="character",age="numeric",gender="character"),
methods = list(
  changeContact=function(cont){
  contact <<- cont  #non local assignment operator for class variable
  },
  customerDetails= function(){
    cat(age,"\n")
    cat(category,"\n")
    cat(gender,"\n")
  }
  )
)
```
```{r}
c1 =customer(name="Alex",contact="1234567890",category="Sports",age=26,gender="Male")
c1
```
Deriving a new class using customer class 

```{r}
globalCustomers = setRefClass("globalCustomers",fields = list(country="character"),contains = "customer",
                              methods = list(
                                changeAddress = function(value){
                                  country <<- value
                                }
                              ))
globalCustomers

```
```{r}
c2 =globalCustomers(name="John",contact="1234567890",category="Sports",age=26,gender="Male",country="US")
c2
```
```{r}
c2$changeContact("234567890") # using parent class method 
c2
```


```{r}

c2$changeAddress("US") # Accessing its own function
c2

```


