---
title: "Assumptions of Linear Regression"
output: html_notebook
---

## Assumption 1 

### Linearity of varibles 
Data variables should have linear relationship.

parameters of linear regression should be linear.

```{r}
cars
```
```{r}
scatter.smooth(x=cars$speed,y=cars$dist,main="Dist vs Speed")
```
## Assumption 2 

### Mean of residual should be 0 

```{r}
# lm () is used for building linear model 
# formula  dept(y) ~ indep(x) => dist ~ speed
#data => cars 

linear_model = lm(dist ~ speed, data = cars)
mean(linear_model$residuals)

#mean of residual is close to zero 
```
```{r}
summary(linear_model)
```
```{r}
linear_model
```
```{r}
ypred = predict(linear_model,cars)
```
```{r}
ypred
```


## Assumption 3 

### No Autocorrelation of residuals
```{r}
library(ggplot2)
acf(linear_model$residuals)
```

```{r}
pacf(linear_model$residuals)
```

```{r}
lmtest::dwtest(linear_model)
```
H0 = Residuals are not autocorrelated
H1 = Residuals are autocorrelated  
```{r}
if(0.09522 > 0.05){
  print("Residuals are not autocorrelated")
}else{
  print("Residuals are autocorrelated")
}
#p value is less than 0.05 then Ho is rejected and alternate hypothesis is accepted

```
## Assumption 4 

## x variable and residuals are uncorrelated 

```{r}
cor.test(cars$speed,linear_model$residuals)

```
H0 => Residuals and x variable are not correlated
H1 => Residuals and x variable are  correlated
```{r}
if(1 > 0.05){
  print("Residuals and x variable are not correlated")
}else{
  print("Residuals and x variable are  correlated")
}
```
## Assumption 5

### No Multicollinearity
```{r}
mtcars

mt_lm = lm(mpg ~ .,data=mtcars)
mt_lm
```
```{r}
library(corrplot)
corrplot(cor(mtcars[,-1]))
```
```{r}
library(car)
vif(mt_lm)
```
How to rectify 

1. Remove variable which is having high vif 
2. Check correlation between your varibles and keep only one pair with high correlation


```{r}
mt_lm_without_disp = lm(mpg ~ cyl+hp+drat+wt+qsec+vs+am+gear+carb,data=mtcars )
vif(mt_lm_without_disp)
```
## Assumption 6 
### Normality of Residuals 

```{r}
par(mfrow=c(2,2))
plot(linear_model,1)

#Residuals vs Fitted Graph 
#1. Used to check linear assumption  
#conclusion => A horizontal line without distict pattern it indicates linear relationship => good
```
```{r}
plot(linear_model,2)
#Normal Q-Q Plot 
#use : to check the residuals normal distribution 
#conclution  : if residuals points following dash line then it is good => having normal distribution 

```

```{r}
plot(linear_model,3)

#Scale Location Plot 

#spread location plot 
#use : shows spread of residuals along with actual values 
#conclusion: homoscedasticity -> equal variance of residuals gives horizontal line
#heteroscadasticity -> variance is not equal and also gives cone shaped pattern or linear pattern
```
```{r}
plot(linear_model,4)
```
```{r}
plot(linear_model)
#use : identify extreme values impacting models performance 
```


    1. Global Stat This is the overall metric; this states whether the model, as a whole, passes or fails.

    2. Skewness <- measuring the distribution

    3. Kurtosis <- measuring the distribution, outliers, influential data, etc

    4. Link function <- misspecified model, how you linked the elements in the model assignment

    5. Heteroscedasticity <- looking for equal variance in the residuals

```{r}
gvlma::gvlma(linear_model)
```
```{r}
summary(linear_model)

```
```{r}

modelSum= summary(linear_model)
modelSum$coefficients
```
```{r}
estimate = modelSum$coefficients["speed","Estimate"]
estimate

std_err =modelSum$coefficients["speed","Std. Error"]
std_err

tstat= estimate/std_err
tstat

pval = 2*pt(-abs(tstat),df=nrow(cars)-ncol(cars))
pval
```
```{r}
AIC(linear_model) #lower  
BIC(linear_model) #lower 
```
R- square -> higher 
Adj R-Square -> higher 
F-statics -> higher
std Error -> close to zero 
t-statistics -> greater than 1.96 for p value less than 0.05 
AIC -> lower 
BIC -> lower 
MAPE -> lower 
MSE -> lower 
RMSE -> lower 
Min Max Accuracy -> Higher 


